\section{Create and Use Applications with context information}
To build this big network of context aware applications that interact with users without them knowing it, we need to understand some conditions. Because of the mobility of the devices the communication of context information need to be collected and shared with wifi or mobile telecommunications technology. If we look at the infrastructure for an Internet of Things platform, it must scale well to increasing amounts of users and must always be available to these users \cite{Kanter539187}.

Another condition to consider is that a large number of applications should be able to run on one ubiquitous device. The ubiquitous devices has limited performance, even if the evolution of the hardware is going forward. Due to their size it makes it important for an application to be lightweight. Ubiquitous computer devices have limited processing capability, small memory space and have limited battery time. The capability of processing is limited which make them not well suited for computation of intensive tasks. A ubiquitous device also have limited amount of available memory. This two conditions makes it more important to have lightweight applications and services on ubiquitous devices. As mentioned battery time is also limited, for example the battery time is decreased when the device is using a lot of network connection. Therefore it is important to make the applications and services efficient in the use of network communication. 
If we run an context-aware application on a Raspberry Pi we need to consider that the device only have 512 MB ram and that this device should be able to run several instances of similar applications so the footprint from the network communication need to be reduced. 

The applications also need near instant access to context-information. Context-information need to be accessed in real-time to provide updated data from sensors. This cannot be provided with a centralized solution \cite{TheMediaSenseFramework}. Real-time delivery of context-information between endpoints is important to existing and future mobile applications. 
